\subsection{Purpose}
The purpose of the Student\&Company (S\&C) Platform is to create a system that allows Students to find Internships to enhance their education and improve their curriculum, while allowing Companies to find suitable candidates for their internship programs. All of this is done in a simple and efficient way by providing a series of tools to help both parties in the process.\\
S\&C will support the entire lifecycle of the Internship process for both Students and Companies: from the initial matchmaking that can be done automatically by the system through a proprietary Recommendation Process, or obtained by a Student with a Spontaneous Application to a specific internship offer, to the final selection process done through structured interviews created and submitted by Companies directly on the platform.\\% 
In the meantime, Student\&Company will also provide a series of Suggestions to improve CVs published by Students and internship offers published by Companies. The platform will also allow the Universities of Students who are actually doing an internship to monitor the progress of such activities and handle any Complaints if necessary, even by terminating the internship if no other solution to the problem can be found.
\subsubsection{Goals}
\begin{enumerate}[label={\color{titleColor}[G\arabic*]}]
\item Companies would like to advertise the internships they offer.
\item Students would like to autonomously candidate for available internships.
\item Students would like to be matched with internships they might be interested in.
\item Companies would like to perform interviews with suitable students.
\item Students and companies would like to complain, communicate problems, and provide information about an Ongoing Internship.
\item Students and companies would like to be provided with suggestions about how to improve their submission;
\item Universities would like to handle complaints about Ongoing Internships.
\item Students would like to choose which internship to attend from among those for which they passed the interview.
\item Companies would like to select students for the internship position among those who passed the interview.
 
\end{enumerate}


\subsection{Scope}
This section defines the scope of the S\&C platform, highlighting the key features and functionalities that enable interactions among students, companies, and universities.
The main features to provide in order to satisfy all the goals are the following:
\begin{itemize}
\item {\color{titleColor}Advertise Internship:}\\ Companies can publish internships offers that:
    \begin{itemize}
        \item Students can spontaneously apply to;
        \item Recommendation process consider while looking for matches.
    \end{itemize}
\item {\color{titleColor}Insert CV:}\\ Students can provide the platform with their CV that Recommendation Process will consider while looking for matches.
\item {\color{titleColor}Spontaneous Application:}\\ Students can autonomously apply for an available internship offer.
%\item {\color{titleColor}Spontaneous Application Acceptance:}\\ Companies can accept a spontaneous application sent by a Student.
\item {\color{titleColor}Recommendation Process:}\\ The platform automatically finds matches between available CV and Internships. At the end of the process, provides Students and Companies with a match they can accept or refuse.
%\item {\color{titleColor}Matches and Application Monitoring:}\\
%Students and Companies can see and interact with spontaneous applications and  matches concerning them.
\item {\color{titleColor}Interview Process:}\\
    Companies can interview both Student whose Spontaneous Application has been accepted, and Students that accepted a match found by the Recommendation Process the company has accepted too. The outcome of the Interview finalizes the selection process that can lead to a confirmed internship experience.  
{%\item {\color{titleColor}Match Acceptance:}\\ Students and Companies can accept a match proposed by the Recommendation Process.
%\item {\color{titleColor}Interview Management:}\\
    %Companies can create template interviews and start the Interview process with:
    %\begin{itemize} 
    %\item Students whose match with one of their Internship has been accepted by both the parties;
    %\item Students whose spontaneous application with one of their Internship has been accepted by both the parties.
    %\end{itemize}
    %Companies can monitor the state of an interview:
    %\begin{itemize}
        %\item sent: means the Interview process concerning that student has started;
        %\item on-going: means that the student is answering the interview he/she received;
        %\item to-be-evaluated: means that the student has answered all the sections of the interview and the interview needs to be evaluated by the Company;
        %\item negatively-evaluated: means that the interview has been negatively evaluated by the Company and the interview will not lead to a confirmed internship;
        %\item positively-evaluated: means that the interview has been positively evaluated by the Company, and it is waiting to be accepted or refused by the Student;
        %\item refused: means that the Student refused the internship offer and the interview will not lead to a confirmed internship;
        %\item accepted: means that the Student accepted the internship offer and the interview will lead to a confirmed internship. It also implies that all the other evaluated/to-be-evaluated/on-going/sent interviews states concerning that student will be imposed to refused.
    %\end{itemize}
    %Companies can delete previously created template interviews only if all the interviews concerning that template are in a refused/accepted/negatively-evaluated state.
}
\item {\color{titleColor}Internship Handling:}\\
    Students and Companies can complain, communicate problems, provide information about a confirmed internship.\\
    University can monitor a confirmed Internship and handle complaints, communicated problems and provided information.
    Handling a complaint, the University can decide to interrupt the Internship.
\item {\color{titleColor}Suggestion Mechanism:}\\
    The platform provide suggestion to both Students and Companies about the manner they insert respectively their CV and Internships. The suggestion achievement is to allow Students and Companies to perform better in Recommendation Process.
\end{itemize}

\subsubsection{World Phenomena}
\begin{enumerate}[label={\color{titleColor}[WP\arabic*]}]
\item A company wants to advertise its internship.
\item A student wants to apply for an internship.
\item A company wants to accept a suitable recommendation.
\item A company wants to accept a student's spontaneous application.
\item A student wants to accept a suitable recommendation.
\item A company wants to interview a student.
\item A company wants to manage (create, visualize, send, evaluate) its interviews.
\item A student wants to answer questions concerning an interview.
\item A company wants to complain, communicates problem, provide information about an Ongoing Internship.
\item A student wants to complain, communicates problem, provide information about an Ongoing Internship.
\item A student wants to receive suggestions on how to improve his CV.
\item A company wants to receive suggestions on how to improve their internship offers.
\item A university wants to monitor an Ongoing Internship that involves one of their students.
\item A university wants to handle complaints about an Ongoing Internship that involves one of their students.
\item A university wants to interrupt an Ongoing Internship that involves one of their students.
\item A company wants to choose from the students they are interested in the ones to whom they will offer the internship position.
\item A student wants to choose an internship position offer.

\end{enumerate}
\subsubsection{Shared Phenomena}
\paragraph{Shared - By World}
\begin{enumerate}[label={\color{titleColor}[SPW\arabic*]}]
\item A company publish an internship.
\item A student insert his CV.
\item A company accepts a spontaneous application.
\item A student or company monitors his recommendations.
\item A student or a company accepts a recommendation.
\item A company creates interviews for a specific internship.
\item A company sends to a student a previously created interview.
\item A company evaluates a previously sent interview that has been answered by the student.
\item A student answers questions related to an interview.
\item A company sends to a student who passed the interview an internship position offer.
\item A student accepts an internship position offer.
\item A student or company complains, communicates problem, provides information about an Ongoing Internship.
\item A university answers to complaints about Ongoing Internships that involves one of their students.
\item A university interrupts an internship that involves one of their students.
\end{enumerate}
\paragraph{Shared - By Machine}
\begin{enumerate}[label={\color{titleColor}[SPM\arabic*]}]
    \item The platform shows to students available internships.
\item The platform shows to companies available candidates for their internships.
\item The platform shows to students and companies information about their recommendations and spontaneous applications.
\item The platform asks for feedback to improve the recommendation research mechanism.
\item The platform notifies students and companies when a suitable recommendation involving them is found.
\item The platform shows to companies information about their interviews.
\item The platform provides students and companies suggestions about how to formulate better respectively their CV and internship offers.
\item The platform shows to universities information about an Ongoing Internship.
\item The platform notifies companies when there is a new spontaneous application regarding one of their internships.
\item The platform notifies a student when a company accepts his spontaneous application.
\item The platform notifies a student when a company sends to him a new interview.
\item The platform notifies a student when a company evaluates an interview he previously sent.
\item The platform notifies a student when a company sends him an internship offer.
\item The platform notifies a company when a student accepts his internship position offer.
\item The platform notifies the involved student and the company when a university terminates their internship.
\item The platform notifies the university when there is a new complaint or problem about an Ongoing Internship regarding one of their students.

\end{enumerate}
\subsection{Definitions, Acronyms, Abbreviations} 
This section offers explanations of terminology to elucidate the terms, acronyms and abbreviations used throughout the document, facilitating easy comprehension and reference for the readers.
\subsubsection{Definition}
\begin{itemize}
    \item \textcolor{titleColor}{\textbf{University}\label{def:university}}: An institution that is registered on the S\&C platform.
    \item \textcolor{titleColor}{\textbf{Company}\label{def:company}}: A company that is registered on the S\&C platform.
    \item \textcolor{titleColor}{\textbf{Student}\label{def:student}}: A person who is currently enrolled in a University and is registered on the S\&C platform.
    \item \textcolor{titleColor}{\textbf{User}\label{def:user}}: Any registered entity on the S\&C platform.
    \item \textcolor{titleColor}{\textbf{Internship Offer}\label{def:internshipOffer}}: The offer of an opportunity to enroll in an internship provided by a Company. The offer remains active on the platform indefinitely until the publishing Company removes it
    \item \textcolor{titleColor}{\textbf{Participant}}\label{def:participant}:{A Participant is an entity that interacts with the platform for the purpose of find or offering an Internship Position Offer, like Students and Companies
    }
    \item \textcolor{titleColor}{\textbf{Recommendation Process}}\label{def:recommendationProcess}: The process of matching a Student with an Internship offered by a Company based on the Student's CV and the Internship's requirements made by the S\&C platform.
    \item \textcolor{titleColor}{\textbf{Recommendation/Match}\label{def:match}}: The result of the Recommendation Process. It is the match between a Student and an Internship.
    \item \textcolor{titleColor}{\textbf{Spontaneous Application}\label{def:spontaneousApplication}}: The process of a Student manually applying for an Internship that was not matched through the Recommendation Process.
    \item \textcolor{titleColor}{\textbf{Interview}\label{def:Interview}}: The process of evaluating a Student's application for an Internship done by a Company through the S\&C platform. 
    \item \textcolor{titleColor}{\textbf{Feedback}\label{def:Feedback}}: Information provided by Participant to the S\&C platform to improve the Recommendation Process.
    \item \textcolor{titleColor}{\textbf{Internship Position Offer}\label{def:internshipPositionOffer}}: The formal offer of an internship position presented to a student who has successfully passed the Interview, who can decide to accept or reject it.
    \item \textcolor{titleColor}{\textbf{Suggestion}\label{def:suggestion}}: Information provided by the S\&C platform to Participant to improve their CVs and Internship descriptions.
    \item \textcolor{titleColor}{\textbf{Confirmed Internship}\label{def:confirmdInternship}}: An Internship that has been accepted by the Student and the offering Company.
    \item \textcolor{titleColor}{\textbf{Ongoing Internship}\label{def:ongoing}}: A internship that is currently in progress. All Ongoing Internships are Confirmed Internships, but the vice versa is not always true.
    \item \textcolor{titleColor}{\textbf{Complaint}\label{def:complaint}}: A report of a problem or issue that a Student or Company has with an Ongoing Internship. It can be published on the platform and handled by the University.
    \item \textcolor{titleColor}{\textbf{Confirmed Match}\label{def:confirmedMatch}}: A match that has been accepted by both a Student and a Company.
    \item \textcolor{titleColor}{\textbf{Rejected Match}\label{def:rejectedMatch}}: A match that has been refused by either a Student or a Company.
    \item \textcolor{titleColor}{\textbf{Pending Match}\label{def:pendingMatch}}: A match that has been accepted only by a Student or a Company, waiting for a response from the other party.
    \item \textcolor{titleColor}{\textbf{Unaccepted Match}\label{def:unacceptedMatch}}: A match that has been refused by either a Student or a Company.

    
    
\end{itemize}

\subsubsection{Acronyms}
\begin{table}[h]
    \centering
\begin{tabular}{|c|c|}
        \hline
        \textbf{Acronyms} & \textbf{Definition} \\ \hline
        RASD & Requirements Analysis \& Specification Document\\ \hline
        CV & Curriculum vitae\\ \hline
    \end{tabular}
    \caption{Acronyms and Definitions}
    \label{tab:acronyms}
\end{table}

\subsubsection{Abbreviations}
\begin{table}[h]
    \centering
\begin{tabular}{|c|c|}
        \hline
        \textbf{Acronyms} & \textbf{Definition} \\ \hline
        S\&C & Students\&Companies \\ \hline
    \end{tabular}
    \caption{Abbreviations and Definitions}
    \label{tab:abbreviations}
\end{table}

\subsection{Revision History}
\begin{table}[h]
    \centering
    \begin{tabular}{|c|c|c|}
        \hline
        \textbf{Revised on} & \textbf{Version} & \textbf{Description}\\ \hline
        ?-?-2024 & 1.0     & Initial release of the document \\ \hline
    \end{tabular}
    \caption{Document Revision History}
    \label{tab:revision_history_table}
\end{table}

\subsection{Reference Documents}
\begin{itemize}
  \item Assignment RDD AY 2024-2025
  \item Software Engineering 2 A.Y. 2024/2025 Slides “CreatingRASD”
  \item IEEE Software Requirements Specification Template
  \item Alloy Documentations: \url{alloy.readthedocs.io}
\end{itemize}


\subsection{Document Structure}
\begin{enumerate}
    \item \textcolor{titleColor}{\textbf{Introduction}}: This section provides an overview of the document and the system. Here the purpose of the platform is explained, along with the goals and phenomena of the system. Finally, essential definitions are provided.
    \item \textcolor{titleColor}{\textbf{Overall Description}}: In this section, a high-level perspective of the system is provided, describing its overall purpose, functionality, and \hyperref[def:user]{User} interactions. It includes an outline of the system's intended features, user profiles, and assumptions about the domain.
    \item \textcolor{titleColor}{\textbf{Specific Requirements}}: In this section, we focus on the technical and functional details of the system. Here, the external interfaces are specified as well as the functional and non-functional requirements of the system. Diagrams, such as use case and sequence diagrams, have been used to provide a visual representation of the system's functionality.
    \item \textcolor{titleColor}{\textbf{Alloy}}: This section illustrates code and diagrams of the Alloy formal specification language that has been used to ensure the consistency and correctness of the system's formalized requirements.
    \item \textcolor{titleColor}{\textbf{Effort Spent}}: This section provides an overview of the time spent by each group member on the project.
    \item \textcolor{titleColor}{\textbf{References}}: This section provides a list of references used in the document.
\end{enumerate}